\Large \bf Uncovering Distributed System Bugs during Testing (not Production!)

### 2015-09-04 paper.tex
added rashmi

%for single author (just remove % characters)
\author{
{\rm Pantazis Deligiannis$^\dagger$, Matt McCutchen$^\diamond$, Paul Thomson$^\dagger$, Shuo Chen$^\star$, Alastair F. Donaldson$^\dagger$}\\
{\rm John Erickson$^\ddagger$, Cheng Huang$^\star$, Akash Lal$^\star$, Shaz Qadeer$^\star$, Wolfram Schulte$^\ddagger$}\\\\
$^\dagger$Imperial College London, $^\ddagger$Microsoft, $^\star$Microsoft Research\\
$^\diamond$Massachusetts Institute of Technology\\
} % end author

>>>>

%for single author (just remove % characters)
\author{
{\rm Pantazis Deligiannis$^\dagger$, Matt McCutchen$^\diamond$, Paul Thomson$^\dagger$, Shuo Chen$^\star$}\\
{\rm Alastair F. Donaldson$^\dagger$, John Erickson$^\ddagger$, Cheng Huang$^\star$, Akash Lal$^\star$}\\
{\rm Rashmi Mudduluru$^\star$, Shaz Qadeer$^\star$, Wolfram Schulte$^\ddagger$}\\\\
$^\dagger$Imperial College London, $^\ddagger$Microsoft, $^\star$Microsoft Research\\
$^\diamond$Massachusetts Institute of Technology\\
} % end author
